---
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the package

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(magrittr)
library(ggplot2)
library(knitr)
library(scales)
```

## Read the Data Set and filter children under 5

```{r}
#read and import the csv file
NSCH_ALL <- read.csv("2019-2020 NSCH_Topical_CAHMI_DRC_v1.2.csv")
#subset to only have children no above age of 5
NSCH <- NSCH_ALL %>% filter(SC_AGE_YEARS <= 5)
```

## function

The function single_table(input) returns a tibble includes:

"Code_index": which is the coding Substitute value, typically: "1" refers to "YES", "2" refers to "NO", "99" refers to "Missing" and "95" refers to "No Answer";

"Counts": the absolute value of number of counts; "Proportion": represents the proportion of this response category in the overall sample; "Percentage": Proportional response into percentage.

This is a reusable function that can be used to obtain a summary table of all factors by entering different vectors.

The format of the input is as follows:

NSCH\$[Variable labels]

[Variable labels] can be found on the Variable labels EXcel Form; and some of the Variables that we are most interesd is listed below:

SC_AGE_YEARS \~ Age of Selected Child - In Years

SC_SEX \~ Sex of Selected Child

SC_RACE_R \~ Race of Selected Child, Detailed

SC_HISPANIC_R \~ Hispanic Origin of Selected Child, Recode

SC_CSHCN \~ Special Health Care Needs Status of Selected Child

HIGRADE \~ Highest Level of Education among Reported Adults

sex_1920 \~ Sex of child

hispanic_1920 \~ Hispanic origin of the child

PrntNativity_1920 \~ Generational status of the parents

HHLanguage_1920 \~ Primary language spoken in the household

povlev4_1920 \~ Income based on federal poverty level status

BornUSA_1920 \~ Children who were born in the United States

NbhdSupp_1920 \~ Indicator 7.1: Children who live in supportive neighborhood

NbhdSafe_1920 \~ Indicator 7.2: Children live in safe neighborhoods

park_1920 \~ Children who live in neighborhoods with a park or playground

RecCentr_1920 \~ Children who live in neighborhoods with recreation center, community center or boys' and girls' club

library_1920 \~ Children who live in neighborhoods with a library or bookmobile

NbhdAmenities_1920 \~ Indicator 7.4: Count of amenities in children's neighborhoods

K4Q27 \~ Needed Health Care Not Received

K5Q10 \~ Need a Referral

DevScrnng_1920 \~ Indicator 4.10: Children who received a developmental screening using a parent-completed screening tool, age 9-35 months

```{r}
#this function RETURN A tibble 
single_table <- function(Code_index){
  mt <- tibble(Code_index)
  
  ans <- mt %>% 
    count(Code_index) %>%
    arrange() %>% 
    mutate(Proportion = n / sum(n)) 

  w <- ans$Proportion
  Percentage <- label_percent()(w)
  ans$Percentage <- Percentage
  colnames(ans)[2] <- "Counts"

  return(ans)
}

```

# Needed Health Care Not Received - K4Q27

# Independent Variables

# Age of children:SC_AGE_YEARS

```{r}
Answer<- c("Under 1 year old", " 1 year old" , " 2 year old", "3 year old", "4 year old", "5 year old")
kable(cbind(single_table(NSCH$SC_AGE_YEARS),Answer),caption = "Age of Selected Child - In Years")
```

# Gender of Children:SC_SEX

```{r}
Answer = c("Male","Female")
kable(cbind(single_table(NSCH$SC_SEX),Answer),caption = "Gender of Children, Detailed")

```

# Race of Children:SC_RACE_R

```{r}

Answer <- c("Hispanic", "White, non-Hispanic", "Black, non-Hispanic" , "Asian, non-Hispanic" ,"American Indian or Alaska Native Non-Hispanic", "Multi-Race Non-Hispanic")
kable(cbind(single_table(NSCH$SC_RACE_R),Answer),caption = "Race of Children, detailed")

```

# Hispanic Children:SC_HISPANIC_R

```{r}

Answer = c("Hispanic", "Non-Hispanic ")
kable(cbind(single_table(NSCH$SC_HISPANIC_R),Answer),caption = "Hispanic Origin of Selected Child")
```

# Special Health needs: SC_CSHCN

```{r}
Answer = c("CSHCN","Non-CSHCN")
kable(cbind(single_table(NSCH$SC_CSHCN),Answer),caption = "Special Health Care Needs Status of Selected Child")
```

# ??????????????Highest Level of Education among Reported Adults: HIGRADE

```{r}
Answer <- c("Less than high school","High school or GED","Some college or technical School","College degree or higher")
kable(cbind(single_table(NSCH$AdultEduc_1920),Answer),caption = "Highest Level of Education among Reported Adults")
```

# sex of children? : sex_1920

```{r}
Answer = c("Male", "Female")
kable(cbind(single_table(NSCH$sex_1920),Answer),caption = "sex of children")
```

#Hispanic origin of the child：hispanic_1920

```{r}
kable(cbind(single_table(NSCH$hispanic_1920)),caption = "Hispanic origin of the child")
```

# Generational status of the parents： PrntNativity_1920

```{r}
Answer = c("All parents born in US","Any parent born outside US","Other","Missing")
kable(cbind(single_table(NSCH$PrntNativity_1920),Answer),caption = "Generational status of the parents")
```

# Primary language spoken in the household

```{r}
Answer<- c("English", "Other than English" , "MISSING")
kable(cbind(single_table(NSCH$HHLanguage_1920),Answer),caption = "Primary language spoken in the household")
```

# Income above poverty: povlev4_1920

```{r}
Answer = c("0-99%FPL","100-199%FPL","200-399FPL","400%FPL or greater")
kable(cbind(single_table(NSCH$povlev4_1920),Answer),caption = "Income based on federal poverty level status")
```

# Children who were born in the United States: BornUSA_1920

```{r}
Answer<- c("All parents born in US", "Any parent born outside of US" , "MISSING")
kable(cbind(single_table(NSCH$BornUSA_1920),Answer),caption = "Children who were born in the United States")
```

# Children who live in supportive neighborhood:NbhdSupp_1920

```{r}
Answer<- c("YES", "NO" , "MISSING")
kable(cbind(single_table(NSCH$NbhdSupp_1920),Answer),caption = "Indicator 7.1: Children who live in supportive neighborhood")
```

# Children live in safe neighborhoods: NbhdSafe_1920

```{r}
Answer<- c("Definitely agree", "Somewhat agree" , "Somewhat disagree", "MISSING")
kable(cbind(single_table(NSCH$NbhdSafe_1920),Answer),caption = "Indicator 7.2: Children live in safe neighborhoods")
```

# Children who live in neighborhoods with a park or playground: park_1920

```{r}
Answer<- c("YES", "NO" , "MISSING")
kable(cbind(single_table(NSCH$park_1920),Answer),caption = "Children who live in neighborhoods with a park or playground")
```

# Children who live in neighborhoods with recreation center, community center or boys' and girls' club:

# RecCentr_1920

```{r}
Answer<- c("YES", "NO" , "MISSING")
kable(cbind(single_table(NSCH$RecCentr_1920),Answer),caption = "Children who live in neighborhoods with recreation center, community center or boys’ and girls’ club")
```

# Children who live in neighborhoods with a library or bookmobile: library_1920

```{r}
Answer<- c("YES", "NO" , "MISSING")
kable(cbind(single_table(NSCH$library_1920),Answer),caption = "Children who live in neighborhoods with a library or bookmobile")
```

# Count of amenities in children's neighborhoods: NbhdAmenities_1920

```{r}
Answer<- c("Doesn't contain any amenties", "Contains 1 amenity" , "Contains 2 amenity", "Contains 3 amenity", "Contains 4 amenity", "MISSING")
kable(cbind(single_table(NSCH$NbhdAmenities_1920),Answer),caption = "Indicator 7.4: Count of amenities in children's neighborhoods")
```

# Outcome Variable

# Needed Health Care Not Received: K4Q27

```{r}
Answer<- c("Didn't receive health care", "Received needed health care" , "MISSING")
kable(cbind(single_table(NSCH$K4Q27),Answer),caption = "Needed Health Care Not Received")
```

# Need a Referral: K5Q10

```{r}
Answer<- c("Need a referral", "Didn't need a referral" , "MISSING")
kable(cbind(single_table(NSCH$K5Q10),Answer),caption = "Need a Referral")
```

# Children who received a developmental screening using a parent-completed

# screening tool, age 9-35 months: DevScrnng_1920

```{r}
Answer<- c("Yes to both types or yes to one and missing to another type", "No to at least one type" , "Children age 0-8 months or 2-5 years","MISSING")
kable(cbind(single_table(NSCH$DevScrnng_1920),Answer),caption = "Screen")
```
