---
title: "Titiana"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this section of the report, we focus on the factors that influence whether children are getting the health cares they need. We will be using the dataset :2019-2020 National Survey of Children's Health (NSCH) from

<https://www.childhealthdata.org/dataset/download?rq=11786>

## Section Enviroment; package used for this setcion

```{r}
# Library(???)
library(readr)
library(likert)
library(ggplot2)
library(xtable)
library(dplyr)
library(ggplot2)
library(stringr)
library(knitr)
```

We will interested in childrens under the age of 5, so we subset the dataset and have a summary statistic to preview it.

```{r}
# read file
NSCH <- read_csv("2019-2020 NSCH_Topical_CAHMI_DRC_v1.2.csv")

# 5 year age
n5 <- length(which(NSCH$SC_AGE_YEARS <=5))
nother <- nrow(NSCH)-n5
NSCH <- subset(NSCH,SC_AGE_YEARS <=5)

```

```{r}
data <- data.frame(
  category=c("Age 5 or younger", "Others"),
  count=c(n5, nother)
)
 
# Compute percentages
data$fraction <- data$count / sum(data$count)

# Compute the cumulative percentages (top of each rectangle)
data$ymax <- cumsum(data$fraction)

# Compute the bottom of each rectangle
data$ymin <- c(0, head(data$ymax, n=-1))

# Compute label position
data$labelPosition <- (data$ymax + data$ymin) / 2

# Compute a good label
data$label <- paste0(data$category, "\n value: ", data$count)

# Make the plot
ggplot(data, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect() +
  geom_label( x=3.5, aes(y=labelPosition, label=label), size=6) +
  scale_fill_brewer(palette=4) +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none")
```

```{r}

length(which(NSCH$K4Q27 == 99))

NSCH <- subset(NSCH, K4Q27 != 99)

```

For Question: During the past 12 months, was there any time when this child needed

health care but it was not received?

```{r,results = 'asis'}
YES <- subset(NSCH,K4Q27 == 1)
NO <- subset(NSCH,K4Q27 == 2)
Missing <- subset(NSCH,K4Q27 == 99)

nyes = nrow(YES)
nno = nrow(NO)
nomiss = nrow(Missing)

# Create test data.
data <- data.frame(
  category=c("Received", "Not Received", "Missing"),
  count=c(nyes, nno, nomiss)
)

data$fraction = y = formatC(data$count/ sum(data$count), digits = 2, format = "f")
 
kable(data,caption = "Answer Sumary")

```

```{r}
y <- NSCH$K4Q27
unique(NSCH$K4Q27)

length(which(y == 99))

# 1 "Did not receive needed health care"
# 2 "Received needed health care (or did not need health care)"
# 99 "Missing".
```

#Plot1 - parent educ

```{r}
edu <- NSCH$AdultEduc_1920
# 1 "Less than high school"
# 2 "High school or GED"
# 3 "Some college or technical school"
# 4 "College degree or higher"

sex <- NSCH$sex_1920
# 1 "Male"
# 2 "Female"

md1 <- data.frame(y,edu,sex)

```

```{r}
md11 <- subset(md1,y ==1)
md12 <- subset(md1,y ==2)

n <- nrow(md11)

edu_1_1 = length(which(md11$edu == 1))/n
edu_1_2 = length(which(md11$edu == 2))/n
edu_1_3 = length(which(md11$edu == 3))/n
edu_1_4 = length(which(md11$edu == 4))/n

edu_1_total = c(edu_1_1,edu_1_2,edu_1_3,edu_1_4)
edu_1_name = c("Less than high school","High school or GED","Some college or technical school","College degree or higher")

data <- data.frame(
  group=edu_1_name,
  value=edu_1_total
)

md <- data.frame(
  Less_than_high_school = 0.02743142,
  High_school_or_GED = 	0.13216958,
  Some_college_or_technical_school = 0.23940150,
  College_degree_or_higher = 0.60099751,
  group = "not received"
)
md
```

```{r}
n <- nrow(md12)

edu_2_1 = length(which(md12$edu == 1))/n
edu_2_2 = length(which(md12$edu == 2))/n
edu_2_3 = length(which(md12$edu == 3))/n
edu_2_4 = length(which(md12$edu == 4))/n

edu_2_total = c(edu_2_1,edu_2_2,edu_2_3,edu_2_4)


md[2,] = c(edu_2_1,edu_2_2,edu_2_3,edu_2_4,"Received")


md2 <- mutate_all(md, function(x) as.numeric(as.character(x)))
md2
```

```{r}
w <-c(0.02743142,0.1321696,0.2394015,0.6009975,0.02085747,0.1147161,0.2069122,0.6575142)
df2 <- data.frame(supp=rep(c("not receive", "received"), each=4),
                dose=rep(c("Less_than_high_school", "High_school_or_GED", "Some_college_or_technical_school","College_degree_or_higher"),2),
                len=w)
```


```{r}
# Stacked barplot with multiple groups
ggplot(data=df2, aes(x=dose, y=len, fill=supp)) +
  geom_bar(stat="identity")
# Use position=position_dodge()
ggplot(data=df2, aes(x=dose, y=len, fill=supp)) +
geom_bar(stat="identity", position=position_dodge())
```

```{r}
a <- nrow(YES)
b <- nrow(NO)
md2[1,] = md2[1,]*a
md2[2,] = md2[1,]*b

rownames(md2) = c("NotReceived" , "Received")
kable(md2)

```



#Plot2

```{r}

park <- NSCH$park_1920
#Children who live in neighborhoods with a park or playground
# 1 "Yes"
# 2 "No"
RecCentr <- NSCH$RecCentr_1920
#Children who live in neighborhoods with recreation center, community center or boys’ and girls’ club
# 1 "Yes"
# 2 "No"
library <- NSCH$library_1920
#Children who live in neighborhoods with a library or bookmobile
# 1 "Yes"
# 2 "No"
NbhdAmenities <- NSCH$NbhdAmenities_1920
#Indicator 7.4: Count of amenities in children's neighborhoods
# 0 "Neighborhood does not contain any amenities" 
# 1 "Neighborhood contains 1 amenity"
# 2 "Neighborhood contains 2 amenities"
# 3 "Neighborhood contains 3 amenities"
# 4 "Neighborhood contains all 4 amenities"

md2 <- data.frame(y,park,RecCentr,library,NbhdAmenities)

```

```{r}
# drop all missing values
missing <-unique(which(md2[,2:5] == 99))
md2<-md2[-missing,]

```

```{r}

no2 <- subset(md2,y == 2)-1
yes2 <- subset(md2,y == 1)-1
```

```{r}
value<-1:6

value[1] = 1-sum(yes2$park)/nrow(yes2)
value[2] = 1-sum(no2$park)/nrow(no2)

value[3] = 1-sum(yes2$RecCentr)/nrow(yes2)
value[4] = 1-sum(no2$RecCentr)/nrow(no2)

value[5] = 1-sum(yes2$library)/nrow(yes2)
value[6] = 1-sum(no2$library)/nrow(no2)
```

```{r}
# create a dataset
Public_Utilities <- c(rep("park" , 2) , rep("library" , 2) , rep("recreation center" , 2) )
Group <- rep(c("Received" , "Not Receive") , 3)
Ratio <- value
data <- data.frame(Public_Utilities,Group,Ratio)
# Grouped
ggplot(data, aes(fill=Group, y=Ratio, x=Public_Utilities)) + 
    geom_bar(position="dodge", stat="identity")
```

